Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-21 NEUROC/sec4-experiments.tex
更新实验图像。

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gcn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GCN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gcn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_ggnn.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GGNN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gat.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GAT.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gat}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{figs/experiments/exp_hyperparameter_on_vertex_edge_phase_time_gaan.pdf}
    \caption{Effects of hyper-parameters on the vertex/edge calculation time of GaAN.}
    \label{fig:exp_hyperparameter_on_vertex_edge_phase_time_gaan}
\end{figure}
